\large Detailed Response to Referees

### 2023-06-18 reports/response1.tex
revise the paper based on the reports

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We try our best to proofread the manuscript carefully.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

>>>>

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this comment. We replace ``Stabilization-Free Virtual Element Methods'' by 
``Virtual Element Methods Without Extrinsic Stabilization'' in the revised manuscript.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. By the numerical results on the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
matrix,
the VEMs without extrinsic stabilization are competitive with respect to other existing VEMs.
Now we emphasize that
\begin{itemize}
\item
In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
\item 
Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
\end{itemize}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
The theoretical part in [15] still has some problems as pointed out by another referee, and [15] is unpublished. We decide to remove the citation of paper [15] and papers depending on [15].

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Any completion of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ can be used for the enhancing constraint.
But we use the orthogonal complement space $\mathbb P_{k-2}^{\perp}(K)$ of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
With the orthogonal complement space $\mathbb P_{k-2}^{\perp}(K)$ for the enhancing constraint, it holds the following identity for the $L^2$ projection
\begin{equation}\label{eq:QKPik}  
Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv.
\end{equation}
Then we can compute the $L^2$ projection $Q_k^Kv$ by the right hand side of \eqref{eq:QKPik}.
The identity \eqref{eq:QKPik} is not true for other choices of complement spaces.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have emphasized it Lemma 4.4.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We rewrite Theorem 4.9 and its proof.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. The performance of our VEMs and other existing VEMs is similar for simple benchmarks.
Now we emphasize that
\begin{itemize}
\item
In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
\item 
Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
\end{itemize}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. Now we remove the citation of paper [15], and the references depending on [15].
